Through the eyes of the teacher - Multimodal exploration of expertise differences

### 2024-10-18 02_paper/02_study/02_expertise_paper/expertise_2024_09_26_no_outlierdetection_MK.Rmd
x paper

library(needs)
needs(tidyverse,
      lubridate,
      viridis,
      grid,
      gridExtra,
      cowplot,
      readxl,
      ARTofR,
      moments,
      ltm,
      sjPlot,
      kableExtra,
      xtable,
      DescTools,
      formattable,
      psych,
      apaTables)

@@

# Statistical Methods for Outlier Detection
# IQR method for outlier detection
# Z-score method for outlier detection
z_scores <- scale(df_aoi_sum) # Standardizing the data
outliers <- df_aoi_sum[abs(z_scores) > 3]

@@

# filter group, participants, total duration & number fixation in entire micro-teaching unit
df_aoi_sum %>%
  group_by(Group) %>% 
  mutate(
    GRI = round(Average_duration_mtu / Sum_number_fixation, digits = 2),
    )-> df_gri

@@

# plotting number of fixations on ALL AOIS
df_gri %>%
  ggplot(mapping = aes(x = Group, y = GRI)) +
  geom_boxplot(mapping = aes(fill = Group), outlier.shape = NA) +
  geom_point(
    size = 2,
    alpha = 0.7,
    position = position_jitter(
      seed = 1,
      width = 0.1,
      height = 0.1
    )
  ) +
  ylim(0, 1) +
  labs(x = "", y = "mean duration of fixations/\nmean number of fixations") +
  scale_fill_brewer(palette  = "RdBu") +
  ggtitle("GRI\n(micro-teaching unit)") +
  theme_cowplot() +
  theme(legend.position = "none") -> plot_gri_group

@@

df_aoi %>% 
  filter(TOI %in% c("Chatting_with_neighbour",
                    "Clicking_pen",
                    "Drawing",
                    "Drumming_with_hands",
                    "Head_on_table",
                    "Heckling",
                    "Looking_at_phone",
                    "Snipping_with_fingers",
                    "Whispering"
                    )
         ) %>% 
  dplyr::select(Participant,
                TOI,
                Time_to_first_fixation.Disruptive_Person,
                ) %>% 
  rowwise() %>% 
  drop_na() %>% 
  group_by(Participant) %>% 
  filter(!Time_to_first_fixation.Disruptive_Person == 0,
         !Time_to_first_fixation.Disruptive_Person > 30000) %>% # cut-off 30sec
  summarise(N = n(),
            Time_to_first_fixation.Disruptive_Person_Sum = sum(Time_to_first_fixation.Disruptive_Person/N)
            ) %>% 
  mutate(Group = ifelse(Participant < 200, "Novice", "Expert"),
         Disrup_time_fixation_sec = round(Time_to_first_fixation.Disruptive_Person_Sum / 1000, 
                                          digits = 2)) -> df_ttff_disrup # changing milliseconds into seconds

# M, SD, min, max time to first fixation "Disruptive Person"
ttff.disrup.table <-
  df_ttff_disrup %>%
  group_by(Group) %>%
  summarise(
    N = n(),
    "M in sec" = round(mean(Disrup_time_fixation_sec), digits = 2),
    "SD in sec" = round(sd(Disrup_time_fixation_sec), digits = 2),
    "Min in sec" = round(min(Disrup_time_fixation_sec), digits = 2),
    "Max in sec" = round(max(Disrup_time_fixation_sec), digits = 2)
  )

@@

##################### plotting time to first fixation for groups ##################### 
plot_time_disrup <- 
  ggplot(data = df_ttff_disrup,
         mapping = aes(x = Group,
                       y = Disrup_time_fixation_sec)) +
 geom_boxplot(mapping = aes(fill = Group),
               outlier.shape = NA) +
  geom_point(size = 2,
             alpha = 0.7,
             position = position_jitter(seed = 1,
                                        width = 0.1,
                                        height = 0.1)) +
  ylim(0,14) +
  labs(x ="",
       y = "Seconds") + 
  scale_fill_brewer(palette  = "RdBu") +
  ggtitle("Time to first fixation\n(AOI disruptive person)") +
  theme_cowplot() +
  theme(legend.position="none")

plot_time_disrup
```

@@

# average duration, number fixation, GRI (micro-teaching unit)
df_aoi %>%
  filter(TOI == "Lesson") %>% 
  dplyr::select(
    Duration_of_interval,
    Participant,
    starts_with("Total_duration_of_fixations"),
    starts_with("Number_of_fixations"),
    starts_with("Average_duration"),
    !"Total_duration_of_fixations.Disruptive_Person",
    !"Number_of_fixations.Disruptive_Person",
    !"Average_duration_of_fixations.Disruptive_Person"
  ) %>%
  rowwise() %>%
  transmute(
    Participant = Participant,
    Duration_of_interval = Duration_of_interval, 
    Duration_of_interval_min = round(Duration_of_interval/60000, digits = 2),
    Sum_duration_fixation = sum(c_across(starts_with("Total_duration")), na.rm = TRUE),
    Sum_average_duration_fixation = sum(c_across(starts_with("Average_duration")), na.rm = TRUE),
    Sum_number_fixation = sum(c_across(starts_with("Number_of")), na.rm = TRUE),
    Average_duration_mtu = round(Sum_duration_fixation / Sum_number_fixation, digits = 0),
    Number_fixation_min_mtu = round(Sum_number_fixation / Duration_of_interval_min, digits = 0),
    GRI_mtu = round(Average_duration_mtu / Sum_number_fixation, digits = 2)
    ) %>%
  drop_na() %>% 
  dplyr::select(Participant,
         Number_fixation_min_mtu, 
         Average_duration_mtu,
         GRI_mtu) -> df_aoi_numb_dur

@@

# time to first fixatoin (AOI disruptive person)
df_aoi %>%
  filter(
    TOI %in% c(
      "Chatting_with_neighbour",
      "Clicking_pen",
      "Drawing",
      "Drumming_with_hands",
      "Head_on_table",
      "Heckling",
      "Looking_at_phone",
      "Snipping_with_fingers",
      "Whispering"
    )
  ) %>%
  dplyr::select(Participant, TOI, Time_to_first_fixation.Disruptive_Person, ) %>%
  rowwise() %>%
  drop_na() %>%
  group_by(Participant) %>%
  summarise(
    Time_to_first_fixation.Disruptive_Person_Sum = sum(Time_to_first_fixation.Disruptive_Person)
  ) %>%
  mutate(
    Group = ifelse(Participant < 200, "Novice", "Expert"),
    Disrup_time_fixation_sec = round(Time_to_first_fixation.Disruptive_Person_Sum / 1000,
      digits = 2
    )
  ) -> df_ttff_disrup

# rating scales
df_sri <-
  excel_sheets("data/Coding_SRI.xlsx") %>%
  map_df(~ read_xlsx("data/Coding_SRI.xlsx", .)) %>%
  filter(
    !ID %in% c(201,
               223),
    !disruption_appraisal == -100,
    !confidence_appraisal == -100,
    !disruption_appraisal == -99,
    !confidence_appraisal == -99,
    !disruption_appraisal == -88,
    !confidence_appraisal == -88,
    !prevalence_rating == -100,
    !prevalence_rating == -99,
    !prevalence_rating == -88
    ) %>% 
  rename(Participant = ID) %>%
  group_by(Participant) %>% 
  summarise(
    Mean_disrupption_appraisal = round(mean(disruption_appraisal), 2),
    Mean_confidence_appraisal = round(mean(confidence_appraisal), 2),
    Mean_prevalence_rating = round(mean(prevalence_rating), 2)
    )%>% 
  dplyr::select(Participant,
                Mean_disrupption_appraisal,
                Mean_confidence_appraisal,
                Mean_prevalence_rating)

# sjt
df_sjt <-
  read_excel("./data/SJT.xlsx") %>%
  dplyr::select(UI06_05, # Participant
                SJT_AL_gek, # Monitoring
                SJT_ST_gek, # Managing momentum
                SJT_R_gek, # Rules and routines
                SJT_KF_gek) %>% # All
  filter(!UI06_05 %in% c(201, 223)) %>%  # exclude ID with no eye tracking data
  transmute(
    Participant = UI06_05,
    SJT_Monitoring = round(SJT_AL_gek, 2),
    SJT_Managing_momentum = round(SJT_ST_gek, 2),
    SJT_Rules_routines = round(SJT_R_gek, 2),
    SJT_All = round(SJT_KF_gek, 2)
  )

@@

# create a big data frame with all measures 
# put all data frames into list
df_list <- list(df_demo,
                df_aoi_numb_dur,
                df_aoi_stud,
                df_aoi_disrup,
                df_sri,
                df_sjt,
                df_quest)

# merge all data frames in list
df_merge <-
  df_list %>% reduce(full_join, by='Participant') %>%
  # filter(Participant > 200) %>% 
  dplyr::select(.,
                -"Participant")

@@

# create a scatter plot 
# pairs(~ Gender + 
#         Age + 
#         `Teaching Experience` + 
#         Sum_number_fixation + 
#         Stud_number_fixation + 
#         Number_of_fixations.Disruptive_Person + 
#         Average_duration_mtu + 
#         Average_duration_stud + 
#         Average_duration_disrup + 
#         GRI_mtu + 
#         GRI_stud + 
#         GRI_disrup + 
#         Mean_disrupption_appraisal + 
#         Mean_confidence_appraisal + 
#         Mean_prevalence_rating + 
#         SJT_Monitoring + 
#         SJT_Managing_momentum + 
#         SJT_Rules_routines + 
#         SJT_All + 
#         Quest_classroom_management + 
#         Quest_non_paraverbal_communication + 
#         Quest_All,
#       upper.panel = NULL,
#       pch = 20,
#       cex = 3, 
#       main = "Correlation Table Expertise Measures",
#       col = Gender)

# apa.cor.table(cor_tab)

>>>>

library(needs)
needs(tidyverse,
      lubridate,
      viridis,
      grid,
      gridExtra,
      cowplot,
      readxl,
      ARTofR,
      moments,
      ltm,
      sjPlot,
      kableExtra,
      xtable,
      DescTools,
      formattable,
      psych,
      apaTables,
      rstatix)

@@

@@

# filter group, participants, total duration & number fixation in entire micro-teaching unit
df_aoi_sum %>%
  group_by(Group) %>% 
  mutate(
    GRI = round(Average_duration_mtu / Number_fixation_min_mtu, digits = 2),
    )-> df_gri

@@

# plotting number of fixations on ALL AOIS
df_gri %>%
  ggplot(mapping = aes(x = Group, y = GRI)) +
  geom_boxplot(mapping = aes(fill = Group), outlier.shape = NA) +
  geom_point(
    size = 2,
    alpha = 0.7,
    position = position_jitter(
      seed = 1,
      width = 0.1,
      height = 0.1
    )
  ) +
  ylim(0, 12) +
  labs(x = "", y = "average duration of fixations/\nnumber of fixations per minute") +
  scale_fill_brewer(palette  = "RdBu") +
  ggtitle("GRI\n(micro-teaching unit)") +
  theme_cowplot() +
  theme(legend.position = "none") -> plot_gri_group

@@

df_aoi %>% 
  filter(TOI %in% c("Chatting_with_neighbour",
                    "Clicking_pen",
                    "Drawing",
                    "Drumming_with_hands",
                    "Head_on_table",
                    "Heckling",
                    "Looking_at_phone",
                    "Snipping_with_fingers",
                    "Whispering"
                    )
         ) %>% 
  dplyr::select(Participant,
                TOI,
                Time_to_first_fixation.Disruptive_Person,
                ) %>% 
  rowwise() %>% 
  drop_na() %>% 
  group_by(Participant) %>% 
  filter(!Time_to_first_fixation.Disruptive_Person == 0, # exclude all participants with 0 msec
         !Time_to_first_fixation.Disruptive_Person > 30000) %>% # cut-off 30sec
  summarise(N = n(),
            Time_to_first_fixation.Disruptive_Person_Sum = sum(Time_to_first_fixation.Disruptive_Person/N)
            ) %>% 
  mutate(Group = ifelse(Participant < 200, "Novice", "Expert"),
         Sum_disruptions = sum(N),
         Disrup_time_fixation_sec = round(Time_to_first_fixation.Disruptive_Person_Sum / 1000, 
                                          digits = 2)) -> df_ttff_disrup # changing milliseconds into seconds

############### M, SD, min, max time to first fixation "Disruptive Person"
ttff.disrup.table <-
  df_ttff_disrup %>%
  filter(!Participant %in% c("216", "113", "123")) %>% 
  group_by(Group) %>%
  summarise(
    N = n(),
    "M in sec" = round(mean(Disrup_time_fixation_sec), digits = 2),
    "SD in sec" = round(sd(Disrup_time_fixation_sec), digits = 2),
    "Min in sec" = round(min(Disrup_time_fixation_sec), digits = 2),
    "Max in sec" = round(max(Disrup_time_fixation_sec), digits = 2)
  )

@@

############### M, SD, min, max of the perceived "Disruptive Person" ############### 
number.perceived.disrup.table <-
 df_ttff_disrup %>%
  filter(!Participant %in% c("216", "113", "123")) %>%
  group_by(Group) %>%
  summarise(
    Mean = round(mean(N, na.rm = TRUE), digits = 2),
    SD = round(sd(N, na.rm = TRUE), digits = 2), 
    Min = min(N, na.rm = TRUE),
    Max = max(N, na.rm = TRUE)
  )

knitr::kable(number.perceived.disrup.table,
             caption = "N, M, SD, min & max of the perceived ´disruptive person´")

############### PLOTTING ###############

##################### plotting "perceived disruptive person" for groups ##################### 
plot_n_disrup <- 
  df_ttff_disrup %>%
  filter(!Participant %in% c("216", "113", "123")) %>%
  ggplot(mapping = aes(x = Group,
                       y = N)) +
 geom_boxplot(mapping = aes(fill = Group),
               outlier.shape = NA) +
  geom_point(size = 2,
             alpha = 0.7,
             position = position_jitter(seed = 1,
                                        width = 0.1,
                                        height = 0.1)) +
  ylim(0,10) +
  labs(x ="",
       y = "Counts") + 
  scale_fill_brewer(palette  = "RdBu") +
  ggtitle("Counts of the perceived ´disruptive person´\n") +
  theme_cowplot() +
  theme(legend.position="none")

plot_n_disrup

##################### plotting time to first fixation for groups ##################### 
plot_time_disrup <- 
  df_ttff_disrup %>%
  filter(!Participant %in% c("216", "113", "123")) %>%
  ggplot(mapping = aes(x = Group,
                       y = Disrup_time_fixation_sec)) +
 geom_boxplot(mapping = aes(fill = Group),
               outlier.shape = NA) +
  geom_point(size = 2,
             alpha = 0.7,
             position = position_jitter(seed = 1,
                                        width = 0.1,
                                        height = 0.1)) +
  ylim(0,10) +
  labs(x ="",
       y = "Seconds") + 
  scale_fill_brewer(palette  = "RdBu") +
  ggtitle("Time to first fixation\n(AOI disruptive person)") +
  theme_cowplot() +
  theme(legend.position="none")

plot_time_disrup

@@

# average duration, number fixation, GRI (micro-teaching unit)
df_aoi %>%
  filter(TOI == "Lesson") %>% 
  dplyr::select(
    Duration_of_interval,
    Participant,
    starts_with("Total_duration_of_fixations"),
    starts_with("Number_of_fixations"),
    starts_with("Average_duration"),
    !"Total_duration_of_fixations.Disruptive_Person",
    !"Number_of_fixations.Disruptive_Person",
    !"Average_duration_of_fixations.Disruptive_Person"
  ) %>%
  rowwise() %>%
  transmute(
    Participant = Participant,
    Duration_of_interval = Duration_of_interval, 
    Duration_of_interval_min = round(Duration_of_interval/60000, digits = 2),
    Sum_duration_fixation = sum(c_across(starts_with("Total_duration")), na.rm = TRUE),
    Sum_average_duration_fixation = sum(c_across(starts_with("Average_duration")), na.rm = TRUE),
    Sum_number_fixation = sum(c_across(starts_with("Number_of")), na.rm = TRUE),
    Average_duration_mtu = round(Sum_duration_fixation / Sum_number_fixation, digits = 0),
    Number_fixation_min_mtu = round(Sum_number_fixation / Duration_of_interval_min, digits = 0),
    GRI_mtu = round(Average_duration_mtu / Number_fixation_min_mtu, digits = 2)
    ) %>%
  drop_na() %>% 
  dplyr::select(Participant,
         Number_fixation_min_mtu, 
         Average_duration_mtu,
         GRI_mtu) -> df_aoi_numb_dur

@@

df_aoi %>% 
  filter(TOI %in% c("Chatting_with_neighbour",
                    "Clicking_pen",
                    "Drawing",
                    "Drumming_with_hands",
                    "Head_on_table",
                    "Heckling",
                    "Looking_at_phone",
                    "Snipping_with_fingers",
                    "Whispering"
                    )
         ) %>% 
  dplyr::select(Participant,
                TOI,
                Time_to_first_fixation.Disruptive_Person,
                ) %>% 
  rowwise() %>% 
  drop_na() %>% 
  group_by(Participant) %>% 
  filter(!Time_to_first_fixation.Disruptive_Person == 0, # exclude all participants with 0 msec
         !Time_to_first_fixation.Disruptive_Person > 30000) %>% # cut-off 30sec
  summarise(N = n(),
            Time_to_first_fixation.Disruptive_Person_Sum = sum(Time_to_first_fixation.Disruptive_Person/N)
            ) %>% 
  mutate(Group = ifelse(Participant < 200, "Novice", "Expert"),
         Sum_disruptions = sum(N),
         Disrup_time_fixation_sec = round(Time_to_first_fixation.Disruptive_Person_Sum / 1000, 
                                          digits = 2)) -> df_ttff_disrup # changing milliseconds into seconds

# rating scales
df_sri <-
  excel_sheets("data/Coding_SRI.xlsx") %>%
  map_df(~ read_xlsx("data/Coding_SRI.xlsx", .)) %>%
  filter(
    !ID %in% c(201,
               223),
    !disruption_appraisal == -100,
    !confidence_appraisal == -100,
    !disruption_appraisal == -99,
    !confidence_appraisal == -99,
    !disruption_appraisal == -88,
    !confidence_appraisal == -88,
    !prevalence_rating == -100,
    !prevalence_rating == -99,
    !prevalence_rating == -88
    ) %>% 
  rename(Participant = ID) %>%
  group_by(Participant) %>% 
  summarise(
    Mean_disrupption_appraisal = round(mean(disruption_appraisal), 2),
    Mean_confidence_appraisal = round(mean(confidence_appraisal), 2),
    Mean_prevalence_rating = round(mean(prevalence_rating), 2)
    )%>% 
  dplyr::select(Participant,
                Mean_disrupption_appraisal,
                Mean_confidence_appraisal)

# sjt
df_sjt <-
  read_excel("./data/SJT.xlsx") %>%
  dplyr::select(UI06_05, # Participant
                SJT_AL_gek, # Monitoring
                SJT_ST_gek, # Managing momentum
                SJT_R_gek, # Rules and routines
                SJT_KF_gek) %>% # All
  filter(!UI06_05 %in% c(201, 223)) %>%  # exclude ID with no eye tracking data
  transmute(
    Participant = UI06_05,
    SJT_Monitoring = round(SJT_AL_gek, 2),
    SJT_All = round(SJT_KF_gek, 2),
  ) %>%
  arrange(Participant)

@@

# create a big data frame with all measures 
# put all data frames into list
df_list <- list(df_demo,
                df_aoi_numb_dur,
                df_aoi_stud,
                df_aoi_disrup,
                df_ttff_disrup,
                df_sri,
                df_sjt,
                df_quest)

# merge all data frames in list
df_merge <-
  df_list %>% reduce(full_join, by='Participant') %>%
  # filter(`Teaching Experience` > 0) %>% 
  dplyr::select(Stud_number_fixation_min,
                Average_duration_stud,
                Number_of_fixations.Disruptive_Person,
                Average_duration_disrup,
                Disrup_time_fixation_sec,
                GRI_mtu,
                SJT_All,
                SJT_Monitoring,
                Quest_All
                )

@@

### Teaching experience with only experts
# merge all data frames in list
df_merge_experts <-
  df_list %>% reduce(full_join, by='Participant') %>%
  filter(`Teaching Experience` > 0) %>% 
  dplyr::select(`Teaching Experience`,
                Stud_number_fixation_min,
                Average_duration_stud,
                Number_of_fixations.Disruptive_Person,
                Average_duration_disrup,
                Disrup_time_fixation_sec,
                GRI_mtu,
                SJT_All,
                SJT_Monitoring,
                Quest_All
                )

# create a correlation matrix
cor_tab_experts <- 
  df_merge_experts %>% 
  cor(method = "pearson") %>% 
  round(., digits = 2)

# p-value for GRI x STJ_All
cor.test(df_merge$GRI_mtu, df_merge$SJT_All)

# p-value for GRI x STJ_Monitoring
cor.test(df_merge$GRI_mtu, df_merge$SJT_Monitoring)

# p-value for GRI x Teaching Experience
cor.test(df_merge_experts$GRI_mtu, df_merge_experts$`Teaching Experience`)
